Re-fit

### 2022-07-14 scripts/r/04_refit/refit_jvc.Rmd
Timo models added

# Functional sequence to get relevant info from Rds files
clean_up <- . %>% 
  tidy(effects = "fixed") %>% 
  suppressWarnings() %>% 
  filter(term %in% c("effect_cattypical", "effect_con")) %>% 
  select(term, estimate, se = std.error)

@@

```{r}
#| label: teams
#| echo: false
teams <- tribble(
  ~'team',                  ~"Reviewed", ~'Included', 
  "anomalocaris_ornata",      TRUE,           TRUE,
  "anthracoceros_coronata",   TRUE,           TRUE,
  "arapaima_modularis",       TRUE,           TRUE,
  "comanthina_maculatus",     TRUE,           TRUE,
  "cromileptes_saxatilis",    TRUE,           TRUE,
  "ctenosaura_limax",         TRUE,           FALSE,
  "gnathosaurus_canadensis",  FALSE,          FALSE,
  "gymnothorax_spinulosus",   FALSE,          FALSE,
  "haematopus_fossor",        TRUE,           TRUE,
  "lasionycteris_altavela",   TRUE,           TRUE,
  "linckia_nattereri",        FALSE,          FALSE,
  "lycodes_bradfieldi",       FALSE,          FALSE,
  "naso_cassivellaunos",      FALSE,          FALSE,
  "trapezia_cantonensis",     FALSE,          FALSE,
  "trigonias_lachneri",       FALSE,          FALSE,
  )

@@

```{r}

@@

@@

@@

@@

@@

@@

@@

msa_models <- dir_ls(path = here("data", "analyses", "models"), 
  regexp = ".rds$") %>% 
  as_tibble() %>% 
  transmute(path = value, 
    mod_name = str_remove(path, here("data", "analyses", "models/")), 
    mod_name = str_remove(mod_name, ".rds"), 
    model = map(path, ~ readRDS(file = .))) %>% 
  separate(mod_name, 
    into = c("word1", "word2", "mod_n", "outcome", "typicality"), 
    sep = "_", remove = F) %>% 
  unite(group, word1, word2, sep = "_") %>% 
  select(group, mod_name:model) %>% 
  mutate(sum = map(model, clean_up)) %>% 
  suppressWarnings() 
```

@@

# Simple pandoc table of the models, estimates, se, etc.
msa_models %>% 
  unnest(sum) %>% 
  select(-model) %>% 
  knitr::kable(format = "pandoc")

@@

```{r}
#| label: forest-plot

>>>>

# Functional sequence to get relevant info from Rds files
clean_up <- . %>% 
  tidy(effects = "fixed") %>% 
  suppressWarnings() %>% 
  filter(term %in% c("effect_cattypical", "effect_con")) %>% 
  dplyr::select(term, estimate, se = std.error)

@@

```{r}
#| label: teams
#| echo: false
teams <- tribble(
  ~'team',                  ~"Reviewed", ~'Included', 
  "anomalocaris_ornata",      TRUE,           TRUE,
  "anthracoceros_coronata",   TRUE,           TRUE,
  "arapaima_modularis",       TRUE,           TRUE,
  "comanthina_maculatus",     TRUE,           TRUE,
  "cromileptes_saxatilis",    TRUE,           TRUE,
  "ctenosaura_limax",         TRUE,           FALSE,
  "gnathosaurus_canadensis",  TRUE,           TRUE,
  "gymnothorax_spinulosus",   TRUE,           TRUE,
  "haematopus_fossor",        TRUE,           TRUE,
  "lasionycteris_altavela",   TRUE,           TRUE,
  "linckia_nattereri",        TRUE,           FALSE,
  "lycodes_bradfieldi",       TRUE,           FALSE,
  "naso_cassivellaunos",      TRUE,           TRUE,
  "trapezia_cantonensis",     TRUE,           TRUE,
  "trigonias_lachneri",       TRUE,           TRUE,
  "psittacula_scabriculus",   TRUE,           TRUE, 
  "clione_dorsalis",          TRUE,           TRUE
  )

@@

```{r}
#| label: gnathosaurus_canadensis

# Load teams data
gnathosaurus_canadensis_typ <- read_xlsx(here("data", "analyses", "jvc", 
  "gnathosaurus_canadensis", "typ.xlsx"))

# Refit original model
f_test <- friedman.test(
  y = gnathosaurus_canadensis_typ$median_st_diff, 
  groups = gnathosaurus_canadensis_typ$typicality, 
  blocks = gnathosaurus_canadensis_typ$speaker
  )

MSA_gnathosaurus_canadensis_df <- gnathosaurus_canadensis_typ %>% 
  mutate(median_diff_z = (median_st_diff - mean(median_st_diff)) / sd(median_st_diff),
    effect_cat = as.factor(typicality), 
    effect_cat = C(effect_cat, treatment))

gnathosaurus_canadensis_1_f0diff_cat <- brm(
  median_diff_z ~ effect_cat, 
  data = MSA_gnathosaurus_canadensis_df, 
  cores = 4, threads = threading(2, grainsize = 100), 
  backend = "cmdstanr", seed = 06022016, 
  file = here("data", "analyses", "models", "gnathosaurus_canadensis_1_f0diff_cat")
  )

@@

```{r}
#| label: gymnothorax_spinulosus

gymnothorax_spinulosus_data <- read.csv2(here("data", "analyses", "jvc", "gymnothorax_spinulosus", "Many_speech_final_3.csv"), dec = ".") %>% 
  mutate(measure = vowel_intensity_diff, 
    speaker = as.factor(speaker), 
    trial = as.factor(trial), 
    condition = as.factor(condition), 
    token = as.factor(token), 
    target_colour = as.factor(target_colour))

# Exclusion process
sd_intensity <- sd(gymnothorax_spinulosus_data$vowel_intensity_diff)
min_int_diff <- median(gymnothorax_spinulosus_data$vowel_intensity_diff)-1.5*sd_intensity
max_int_diff <- median(gymnothorax_spinulosus_data$vowel_intensity_diff)+1.5*sd_intensity
gymnothorax_spinulosus_data$exclude <- 0
gymnothorax_spinulosus_data[which(gymnothorax_spinulosus_data$vowel_intensity_diff<min_int_diff),]$exclude <- 1
gymnothorax_spinulosus_data$exclude <- factor(gymnothorax_spinulosus_data$exclude)
gymnothorax_spinulosus_int <- gymnothorax_spinulosus_data[which(gymnothorax_spinulosus_data$exclude==0),]
gymnothorax_spinulosus_int$typ_mean <- gymnothorax_spinulosus_int$typ_mean/100

#
# Fit original model
#
fit0 <- lmer(measure ~ condition * typ_mean + 
    (1|target_colour) + 
    (1|speaker),
  data = gymnothorax_spinulosus_int, 
  REML = FALSE , 
  na.action = na.exclude
  )

# Set up post hoc comparisons
contmat <- rbind(c(0,0,0,1,0,0), c(0,0,0,1,1,0), c(0,0,0,1,0,1))
rownames(contmat) <- c('pente AF','pente ANF','pente NF')
comp_mult <- summary(multcomp::glht(fit0, linfct = contmat))
comp_mult

#
# JVC refits
#
MSA_gymnothorax_spinulosus_df <- gymnothorax_spinulosus_int %>% 
  mutate(measure_z = (measure - mean(measure)) / sd(measure),
    effect_con = (typ_mean - mean(typ_mean)) / sd(typ_mean)) %>% 
  filter(condition == "AF")

gymnothorax_spinulosus_1_intdiff_con <- brm(
  measure_z ~ effect_con + 
    (1|target_colour) + 
    (1|speaker), 
  data = MSA_gymnothorax_spinulosus_df, 
  cores = 4, threads = threading(2, grainsize = 100), 
  backend = "cmdstanr", seed = 06022016, 
  file = here("data", "analyses", "models", "gymnothorax_spinulosus_1_intdiff_con")
  )

@@

```{r}
#| label: linckia_nattereri

linckia_nattereri_dat <- read.csv(here("data", "analyses", "jvc", 
"linckia_nattereri", "ResultsNF2.csv")) %>% 
  mutate(typicality = as.factor(typicality))

# Fit original bayesian models with default priors

NOTE: Fit bayesian logistic regression model (typicality = DV) with 10 continuous predictors. ASK stef and timo for suggestions.

@@

```{r}
#| label: lycodes_bradfieldi

Processed data not available.

@@

```{r}
#| label: naso_cassivellaunos

msa <- read_csv(here("data", "analyses", "jvc", "naso_cassivellaunos", 
  "ProPer_MSA", "data_tables", "ProPer_MSA_scores.csv"))
msa <- msa[msa$syllable %in% c("A_P*", "A_F", "N_P*", "N_F"),]
msa$syllable <- factor(msa$syllable, levels = c("A_P*", "A_F", "N_P*", "N_F"), labels = c("A_Penult", "A_Final", "N_Penult", "N_Final"), ordered = FALSE)
# Set "typical" the 1st / reference level
msa$typicality <- factor(msa$typicality, levels = c("typical", "medium", "atypical"))
# Set "atypical" the 1st / reference level
#msa$typicality <- factor(msa$typicality, levels = c("atypical", "medium", "typical"))

# Reorder target_name wrt typicality
msa$target_name <- factor(msa$target_name)
msa$target_name <- fct_reorder(msa$target_name, as.numeric(msa$typicality))

load(here("data", "analyses", "jvc", "naso_cassivellaunos", 
  "Bayesian analysis", "Mass_Models.rda"))

#
# JVC refit
#

MSA_naso_cassivellaunos_data <- msa %>% 
  mutate(mass_rel_log = log(mass_rel), 
    mass_rel_z = (mass_rel_log - mean(mass_rel_log)) / sd(mass_rel_log), 
    DeltaF0_rel_z = (DeltaF0_rel - mean(DeltaF0_rel)) / sd(DeltaF0_rel), 
    sync_rel_z = (sync_rel - mean(sync_rel)) / sd(sync_rel), 
    effect_cat = C(typicality, treatment), 
    effect_cat = fct_relevel(effect_cat, "atypical"), 
    syllable = C(syllable, sum))

naso_cassivellaunos_1_mass_cat <- brm(
  mass_rel_z ~ effect_cat * syllable +  
    (1 + effect_cat * syllable | speaker), 
  data = MSA_naso_cassivellaunos_data, 
  cores = 4, threads = threading(2, grainsize = 100), 
  backend = "cmdstanr", seed = 06022016, 
  file = here("data", "analyses", "models", "naso_cassivellaunos_1_mass_cat")
  )

naso_cassivellaunos_2_f0delta_cat <- brm(
  DeltaF0_rel_z ~ effect_cat * syllable +  
    (1 + effect_cat * syllable | speaker), 
  data = MSA_naso_cassivellaunos_data, 
  cores = 4, threads = threading(2, grainsize = 100), 
  backend = "cmdstanr", seed = 06022016, 
  file = here("data", "analyses", "models", "naso_cassivellaunos_2_f0delta_cat")
  )

naso_cassivellaunos_3_syncrel_cat <- brm(
  sync_rel_z ~ effect_cat * syllable +  
    (1 + effect_cat * syllable | speaker), 
  data = MSA_naso_cassivellaunos_data, 
  cores = 4, threads = threading(2, grainsize = 100), 
  backend = "cmdstanr", seed = 06022016, 
  file = here("data", "analyses", "models", "naso_cassivellaunos_3_syncrel_cat")
  )

@@

```{r}
#| label: trapezia_cantonensis

if(F) {
msa_raw <- tibble(
  path = Sys.glob(
    glue::glue("{here('./data/analyses/jvc/trapezia_cantonensis/')}/audio_chunks/*/_FastTrack/csvs/*.csv")), 
  file = map(path, read_csv, progress = FALSE, show_col_types = FALSE)) %>%
    unnest(file)

typicality <- tribble(
    ~"adj", ~"noun", ~"typicality",
    "gelben",  "Kirsche", "atypical",
    "gruenen", "Moehre",  "atypical",
    "roten",   "Gurke",   "atypical",
    "orangen", "Trauben", "atypical",
    "braunen", "Paprika", "atypical",
    "gelben",  "Erbsen",     "medium",
    "gruenen", "Tomate",     "medium", 
    "roten",   "Aprikose",   "medium",
    "orangen", "Kartoffeln", "medium",
    "braunen", "Banane",     "medium",
    "gelben",  "Zitrone",   "typical",
    "gruenen", "Bohnen",    "typical",
    "roten",   "Erdbeere",  "typical",
    "orangen", "Mandarine", "typical",
    "braunen", "Walnuss",   "typical",
    "gelben", "Sonnenbrille",   "non-food",
    "gelben", "Socken",         "non-food",
    "gelben", "Waescheklammer", "non-food",
    "gruenen", "Sonnenbrille",   "non-food",
    "gruenen", "Socken",         "non-food",
    "gruenen", "Bueroklammer",   "non-food",
    "roten", "Socken",         "non-food",
    "roten", "Bueroklammer",   "non-food",
    "roten", "Waescheklammer", "non-food",
    "orangen", "Socken",         "non-food",
    "orangen", "Bueroklammer",   "non-food",
    "orangen", "Waescheklammer", "non-food",
    "braunen", "Sonnenbrille",   "non-food",
    "braunen", "Bueroklammer",   "non-food",
    "braunen", "Waescheklammer", "non-food"
)

beast_path <- "/Users/casillas/academia/research/in_progress/many_speech_analyses/many_analyses/./data/analyses/jvc/trapezia_cantonensis//audio_chunks/"

msa_processed <- msa_raw %>% 
  mutate(path = str_remove_all(path, beast_path), 
    path = str_remove_all(path, "/.*/_FastTrack/csvs/"),
    path = str_remove_all(path, "_\\d+\\.csv")) %>% 
    separate(path, into = c("art", "adj", "noun", "speaker_trial"), 
      sep = "_", extra = "merge") %>%
    mutate(noun = str_remove_all(noun, "/")) %>% 
    separate(speaker_trial, into = c("speaker", "trial"), 
      sep = "_(?=\\d+\\Z)") %>%
    # Add the typicality ratings
    left_join(typicality, by = c("adj", "noun")) %>%
    # Get normalized time, and duration
    group_by(speaker, trial) %>%
    mutate(percent = time / max(time),
           dur = max(time) - min(time),
           .after = time) %>%
    ungroup()

msa_for_dur <- msa_processed %>%
  dplyr::select(art, adj, noun, speaker, trial, dur, typicality) %>%
  distinct() %>%
  mutate(typicality = factor(typicality, 
    levels = c("typical", "medium", "atypical", "non-food")))

write_csv(msa_for_dur, 
  file = here("data", "analyses", "jvc", "trapezia_cantonensis", "jvc_tidy.csv"))

dur_lmer <- lmer(
  dur ~ typicality + 
    (1|adj) + (1|speaker), 
  data = msa_for_dur
  )

}

#
# JVC refit
#

MSA_trapezia_cantonensis_data <- read_csv(
  here("data", "analyses", "jvc", "trapezia_cantonensis", "jvc_tidy.csv")
  ) %>% 
  mutate_if(is.character, as.factor) %>% 
  mutate(dur_z = (dur - mean(dur)) / sd(dur), 
    effect_cat = C(typicality, treatment), 
    effect_cat = fct_relevel(effect_cat, "atypical"))

trapezia_cantonensis_4_dur_cat <- brm(
  dur_z ~ effect_cat +  
    (1|adj) + (1|speaker), 
  data = MSA_trapezia_cantonensis_data, 
  cores = 4, threads = threading(2, grainsize = 100), 
  backend = "cmdstanr", seed = 06022016, 
  file = here("data", "analyses", "models", "trapezia_cantonensis_4_dur_cat")
  )

@@

```{r}
#| label: trigonias_lachneri

msa <- read.csv(here("data", "analyses", "jvc", "trigonias_lachneri", 
  "CSV", "whole_no_errors.csv"))

msa_linear <- subset(msa, select = c(participant, spi, speaker, trial, condition, typicality, target_colour,typ_mean))
#correcting variable types in R
msa_linear$participant <- as.factor(msa_linear$participant)
msa_linear$speaker <- as.factor(msa_linear$speaker)
msa_linear$trial <- as.integer(msa_linear$trial)
msa_linear$spi <- as.numeric(msa_linear$spi)
msa_linear$condition <- as.factor(msa_linear$condition)
msa_linear$typicality <- as.factor(msa_linear$typicality)
msa_linear$target_colour <- as.factor(msa_linear$target_colour)

spi_base <- msa_linear %>%
  filter(condition %in% "NF")
spi_base$spi <- log(spi_base$spi)

spi.var.md <- lmer(spi ~ typ_mean + 
    (1 + typ_mean|target_colour) + 
    (1 + typ_mean|speaker), 
  data = spi_base, 
  control=lmerControl(optimizer="bobyqa",optCtrl=list(maxfun=100000)), 
  REML = TRUE)

#
# JVC refit
#

MSA_trigonias_lachneri_spi_data <- spi_base %>% 
  mutate(spi_z = (spi - mean(spi, na.rm = T)) / sd(spi, na.rm = T)) %>% 
  mutate(effect_con = (typ_mean - mean(typ_mean)) / sd(typ_mean))

trigonias_lachneri_1_spi_con <- brm(
  spi_z ~ effect_con, 
  data = MSA_trigonias_lachneri_spi_data, 
  cores = 4, threads = threading(2, grainsize = 100), 
  backend = "cmdstanr", 
  file = here("data", "analyses", "models", "trigonias_lachneri_1_spi_con")
  )

## psittacula_scabriculus

```{r}
#| label: print_psittacula_scabriculus
#| echo: false
#| results: 'asis'
print_status("psittacula_scabriculus")
```

```{r}
#| label: psittacula_scabriculus

MSA_psittacula_scabriculus_raw <- read_xlsx(
  path = here("data", "analyses", "jvc", "psittacula_scabriculus", 
    "Data_and_analysis", "psittacula_scabriculus_full_dataset_checked.xlsx"))

MSA <- MSA_psittacula_scabriculus_raw %>%
  arrange(target_name) %>% #orders the rows of the data by the target_name column
  group_by(target_name) %>% #group by the target name
  transform(items = as.numeric(factor(target_name)))%>% #transform target name into a item
  select(items, target_name, everything()
         ) #select all variables from items and target_name

MSAcomplete <- MSA %>% 
  filter (condition == 'NF') %>% 
  filter (avgdur > 0)

#count notpronounced for each vowel (1,2,3,4)
M_not <- MSAcomplete %>%
  filter(dur1 == "notpronounced"|dur2 == "notpronounced"|dur3 == "notpronounced"|dur4 == "notpronounced")

dur1_not <- M_not%>%
  filter(dur1 == "notpronounced")
dur2_not <- M_not%>%
  filter(dur2 == "notpronounced")
dur3_not <- M_not%>%
  filter(dur3 == "notpronounced")
dur4_not <- M_not%>%
  filter(dur4 == "notpronounced")

#Convert the average duration from character to number. 
MSAcomplete$avgdur <- as.numeric(MSAcomplete$avgdur)

regularizing_priors <- prior('normal(0, 1)', class = 'b')
options(mc.cores=parallel::detectCores())
# Original model
set.seed(42)

if(F) {
MSA_mdl <- brm(
  avgdur ~ 1 + typicality + 
    (1 + typicality |participant) +  
    (1 + typicality |items), 
  data = MSAcomplete, 
  prior = regularizing_priors,  
  seed = 42, init = 0, cores = 4, 
  chains = 4, warmup = 2000, iter = 4000)
}

#
# JVC refit
#

msa_psittacula_scabriculus_df <- MSAcomplete %>% 
  mutate(avgdur_z = (avgdur - mean(avgdur)) / sd(avgdur), 
    effect_cat = as.factor(typicality), 
    effect_cat = C(effect_cat, treatment), 
    effect_cat = fct_relevel(effect_cat, "atypical"))

psittacula_scabriculus_1_dur_cat <- brm(
  avgdur_z ~ effect_cat +  
    (1 + effect_cat | participant) +  
    (1 + effect_cat | items), 
  data = msa_psittacula_scabriculus_df, 
  cores = 4, threads = threading(2, grainsize = 100), 
  backend = "cmdstanr", seed = 06022016, 
  file = here("data", "analyses", "models", "psittacula_scabriculus_1_dur_cat")
  )

## clione_dorsalis

```{r}
#| label: print_clione_dorsalis
#| echo: false
#| results: 'asis'
print_status("clione_dorsalis")
```

```{r}
#| label: clione_dorsalis

#read and clean the data
data_formants_duration <- read.csv(
  here("data", "analyses", "jvc", "clione_dorsalis", 
  "MSA_formantlog.csv"))
data_vs <- read.csv(
    here("data", "analyses", "jvc", "clione_dorsalis", 
    "MSA_formantlog_vowel space area.csv"))

data_no_NA <- subset(data_formants_duration, typicality != "NA")
data_formant_midpoint <- subset(data_no_NA, timept == "3")
data_vs <- plyr::rename(data_vs, c("atypical"="vowel_space_area"))
data_2 <- subset(data_vs, timepoint == "2")
data_4 <- subset(data_vs, timepoint == "4")
formants_tp_2 <- subset(data_no_NA, timept == "2")
formants_tp_4 <- subset(data_no_NA, timept == "4")

# REfit original models
duration.mod <- lmer(word.duration ~ typicality + vowel + gender + (1|filename), data=data_formant_midpoint)

vsa.mod.2 <- lmer(vowel_space_area ~ typicality + (1|subject),data=data_2)
vsa.mod.4 <- lmer(vowel_space_area ~ typicality + (1|subject),data=data_4)

###F1 and F2 models
mod.4 <- lmer(f1 ~ typicality*vowel + gender + (1|filename), data=formants_tp_2)
mod.5 <- lmer(f2 ~ typicality*vowel + gender + (1|filename), data=formants_tp_2)
mod.6 <- lmer(f1 ~ typicality*vowel + gender + (1|filename), data=formants_tp_4)
mod.7 <- lmer(f2 ~ typicality*vowel + gender + (1|filename), data=formants_tp_4)

#
# JVC refit
#
msa_clione_dorsalis_mp <- data_formant_midpoint %>% 
  mutate(
    word_duration_z = (word.duration - mean(word.duration)) / sd(word.duration), 
    effect_cat = as.factor(typicality), 
    effect_cat = C(effect_cat, treatment), 
    effect_cat = fct_relevel(effect_cat, "atypical"), 
    vowel = as.factor(vowel), 
    vowel = C(vowel, sum), 
    gender = as.factor(gender), 
    gender = C(gender, sum)
    )

clione_dorsalis_1_mp_cat <- brm(
  word_duration_z ~ effect_cat + vowel + gender + 
    (1|filename), 
  data = msa_clione_dorsalis_mp, 
  cores = 4, threads = threading(2, grainsize = 100), 
  backend = "cmdstanr", seed = 06022016, 
  file = here("data", "analyses", "models", "clione_dorsalis_1_mp_cat")
  )

msa_clione_dorsalis_vs <- data_2 %>% 
  mutate(
    vowel_space_area_z = (vowel_space_area - mean(vowel_space_area)) / sd(vowel_space_area), 
    effect_cat = as.factor(typicality), 
    effect_cat = C(effect_cat, treatment), 
    effect_cat = fct_relevel(effect_cat, "atypical"), 
  )

clione_dorsalis_2_vs_cat <- brm(
  vowel_space_area_z ~ effect_cat + 
    (1 | subject), 
  data = msa_clione_dorsalis_vs, 
  cores = 4, threads = threading(2, grainsize = 100), 
  backend = "cmdstanr", seed = 06022016, 
  file = here("data", "analyses", "models", "clione_dorsalis_2_vs_cat")
  )

msa_clione_dorsalis_vs4 <- data_4 %>% 
  mutate(
    vowel_space_area_z = (vowel_space_area - mean(vowel_space_area)) / sd(vowel_space_area), 
    effect_cat = as.factor(typicality), 
    effect_cat = C(effect_cat, treatment), 
    effect_cat = fct_relevel(effect_cat, "atypical"), 
  )

clione_dorsalis_3_vs4_cat <- brm(
  vowel_space_area_z ~ effect_cat + 
    (1 | subject), 
  data = msa_clione_dorsalis_vs4, 
  cores = 4, threads = threading(2, grainsize = 100), 
  backend = "cmdstanr", seed = 06022016, 
  file = here("data", "analyses", "models", "clione_dorsalis_3_vs4_cat")
  )

msa_clione_dorsalis_f1f22 <- formants_tp_2 %>% 
  mutate(
    f1_z = (f1 - mean(f1)) / sd(f1), 
    f2_z = (f2 - mean(f2)) / sd(f2), 
    effect_cat = as.factor(typicality), 
    effect_cat = C(effect_cat, treatment), 
    effect_cat = fct_relevel(effect_cat, "atypical"), 
    vowel = as.factor(vowel), 
    vowel = C(vowel, sum), 
    gender = as.factor(gender), 
    gender = C(gender, sum)
  )

clione_dorsalis_4_f12_cat <- brm(
  f1_z ~ effect_cat + vowel + gender + 
    (1|filename), 
  data = msa_clione_dorsalis_f1f22, 
  cores = 4, threads = threading(2, grainsize = 100), 
  backend = "cmdstanr", seed = 06022016, 
  file = here("data", "analyses", "models", "clione_dorsalis_4_f12_cat")
  )

clione_dorsalis_5_f22_cat <- brm(
  f2_z ~ effect_cat + vowel + gender + 
    (1|filename), 
  data = msa_clione_dorsalis_f1f22, 
  cores = 4, threads = threading(2, grainsize = 100), 
  backend = "cmdstanr", seed = 06022016, 
  file = here("data", "analyses", "models", "clione_dorsalis_5_f22_cat")
  )

msa_clione_dorsalis_f1f24 <- formants_tp_4 %>% 
  mutate(
    f1_z = (f1 - mean(f1)) / sd(f1), 
    f2_z = (f2 - mean(f2)) / sd(f2), 
    effect_cat = as.factor(typicality), 
    effect_cat = C(effect_cat, treatment), 
    effect_cat = fct_relevel(effect_cat, "atypical"), 
    vowel = as.factor(vowel), 
    vowel = C(vowel, sum), 
    gender = as.factor(gender), 
    gender = C(gender, sum)
  )

clione_dorsalis_6_f14_cat <- brm(
  f1_z ~ effect_cat + vowel + gender + 
    (1|filename), 
  data = msa_clione_dorsalis_f1f24, 
  cores = 4, threads = threading(2, grainsize = 100), 
  backend = "cmdstanr", seed = 06022016, 
  file = here("data", "analyses", "models", "clione_dorsalis_6_f14_cat")
  )

clione_dorsalis_7_f24_cat <- brm(
  f2_z ~ effect_cat + vowel + gender + 
    (1|filename), 
  data = msa_clione_dorsalis_f1f24, 
  cores = 4, threads = threading(2, grainsize = 100), 
  backend = "cmdstanr", seed = 06022016, 
  file = here("data", "analyses", "models", "clione_dorsalis_7_f24_cat")
  )

@@

msa_models <- dir_ls(path = here("data", "analyses", "models"), 
  regexp = ".rds$") %>% 
  as_tibble() %>% 
  transmute(path = value, 
    mod_name = str_remove(path, here("data", "analyses", "models/")), 
    mod_name = str_remove(mod_name, ".rds"), 
    model = map(path, ~ readRDS(file = .))) %>% 
  separate(mod_name, 
    into = c("word1", "word2", "mod_n", "outcome", "typicality"), 
    sep = "_", remove = F) %>% 
  unite(group, word1, word2, sep = "_") %>% 
  dplyr::select(group, mod_name:model) %>% 
  mutate(sum = map(model, clean_up)) %>% 
  suppressWarnings() 
```

@@

# Simple pandoc table of the models, estimates, se, etc.
msa_models %>% 
  unnest(sum) %>% 
  dplyr::select(-model) %>% 
  knitr::kable(format = "pandoc")

@@

```{r}
#| label: forest-plot
#| fig.height: 8
